%%
%% Template abstract.tex
%%

\chapter*{Abstract}
\label{cha:abstract}
\addcontentsline{toc}{chapter}{Abstract}

The language policy of Q\&A websites has been under the hot debate for a long time and there is still no convincing conclusion. Many of these communities are holding an English-Only Policy but operating some foreign language variants at the same time. Recognizing whether it is meaningful to develop multilingual flagship sites is a fundamental research question, and an advanced method towards bridging the gap between multilingual communities with deep learning can be very attractive to solve this problem. Traditional research on the Q\&A websites focus on the same language or the accuracy of language processing method. However, these methods are not robust to deal with the lexical gap between different languages(e.g. English and Russian). In this paper, we formulate the problem of predicting similarity of question pairs in different languages and solve the problem by deep learning concept. Except for the neural language model we adopt, we mining large amounts of duplicate question pairs from Stack Exchange data dump of September 2017[1] to train deep semantic similarity model (DSSM). The results confirm us the probability and value of developing the cross-lingual deep learning methods, and also show us that this deep-learning approach significantly outperforms traditional methods in the cross-language fields.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis"
%%% End: 
